Counting infinitely by Oritatami co-transcriptional folding

### 2019-08-21 paper.tex
writting encoding...

%\titlerunning{}
\author{
Kohei Maruyama\inst{1}\thanks{Primary corresponding author (\email{k.maruyama@uec.ac.jp})} \and
Shinnosuke Seki\inst{1}\thanks{Secondary corresponding author (\email{s.seki@uec.ac.jp})}
}
\institute{
The University of Electro-Communications, 
%Graduate School of Informatics and Engineering, 
1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan \\
}

@@

Counting is one of the most essential tasks for computing; as well known, it suffices to count for Turing universality \cite{Minsky1967}. 
Nature has been counting billions of days using molecular ``circadian clockwork'' which is ``as complicated and as beautiful as the wonderful chronometers developed in the 18th century''  \cite{McClung2006}. 
Nowadays, developments in molecular self-assembly technology enable us to design molecules to count. 
Evans has recently demonstrated a DNA tile self-assembly system that counts accurately in binary from a programmed initial count until it overflows \cite{EvansPhD}. 
In its foundational theory of molecular self-assembly, such binary counters have proved their versatility, being used to assemble shapes of particular size \cite{AdChGoHu2001,RothemundWinfree2000}, towards self-assembly of fractals \cite{MasudaSekiUbukata2018}, as an infinite scaffold to simulate all Turing machines in parallel in order to prove undecidability of nondeterminism in the abstract tile-assembly model \cite{BrChDoKaSe2013}, and so on.

@@

Let $\Sigma$ be a finite set of types of abstract molecules, or \textit{beads}. 
A bead of type $a \in \Sigma$ is called an $a$-bead. 
By $\Sigma^*$ and $\Sigma^\omega$, we denote the set of finite sequences of beads and that of one-way infinite sequences of beads, respectively. 
The empty sequence is denoted by $\lambda$. 
Let $w = b_1 b_2 \cdots b_n \in \Sigma^*$ be a sequence of length $n$ for some integer $n$ and bead types $b_1, \ldots, b_n \in \Sigma$. 
The \textit{length} of $w$ is denoted by $|w|$, that is, $|w| = n$. %ここから要らない？↓やっぱり要る
For two indices $i, j$ with $1 \le i \le j \le n$, we let $w[i..j]$ refer to the subsequence $b_i b_{i+1} \cdots b_{j-1}b_j$; if $i = j$, then $w[i..i]$ is simplified as $w[i]$. 
For $k \ge 1$, $w[1..k]$ is called a \textit{prefix} of $w$.

Oritatami systems fold their transcript, which is a sequence of beads, over the triangular grid graph $\mathbb{T} = (V, E)$ cotranscriptionally. %↓
We designate one point in $V$ as the origin $O$ of $\mathbb{T}$. 
For a point $p \in V$, let $\hexagon_p^d$ denote the set of points which lie in the regular hexagon of radius $d$ centered at the point $p$. 
Note that $\hexagon_p^d$ consists of $3d(d+1)+1$ points. %←
A directed path $P = p_1 p_2 \cdots p_n$ in $\mathbb{T}$ is a sequence of \textit{pairwise-distinct} points $p_1, p_2, \ldots, p_n \in V$ such that $\{p_i, p_{i+1}\} \in E$ for all $1 \le i < n$. 
Its $i$-th point is referred to as $P[i]$. 
Now we are ready to abstract RNA single-stranded structures in the name of conformation. 
A \textit{conformation} $C$ (over $\Sigma$) is a triple $(P, w, H)$ of a directed path $P$ in $\mathbb{T}$, $w \in \Sigma^*$ of the same length as $P$, and a set of h-interactions $H \subseteq \bigl\{\{i, j\} \bigm| 1 \le i, i+2 \le j, \{P[i], P[j]\} \in E \bigr\}$. 
This is to be interpreted as the sequence $w$ being folded along the path $P$ in such a manner that its $i$-th bead $w[i]$ is placed at the $i$-th point $P[i]$ and the $i$-th and $j$-th beads are bound (by a hydrogen-bond-based interaction) if and only if $\{i, j\} \in H$. 
The condition $i+2 \le j$ represents the topological restriction that two consecutive beads along the path cannot be bound. 
The \textit{length} of $C$ is defined to be the length of its transcript $w$ (that is, equal to the length of the path $P$). 
A \textit{rule set} $R \subseteq \Sigma \times \Sigma$ is a symmetric relation over $\Sigma$, that is, for all bead types $a, b \in \Sigma$, $(a, b) \in R$ implies $(b, a) \in R$.
A bond $\{i, j\} \in H$ is \textit{valid with respect to $R$}, or simply $R$-valid, if $(w[i], w[j]) \in R$. 
This conformation $C$ is \textit{$R$-valid} if all of its bonds are $R$-valid. %↓
For an integer $\alpha \ge 1$, $C$ is \textit{of arity $\alpha$} if it contains a bead that forms $\alpha$ bonds but none of its beads forms more. 
By $\mathcal{C}_{\le \alpha}(\Sigma)$, we denote the set of all conformations over $\Sigma$ whose arity is at most $\alpha$; its argument $\Sigma$ is omitted whenever $\Sigma$ is clear from the context.

@@

An \textit{oritatami system} (OS) $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ is composed of
\begin{itemize}
\item a set $\Sigma$ of bead types, 
\item a rule set $R \subseteq \Sigma \times \Sigma$, 
\item a positive integer $\delta$ called the \textit{delay}, 
\item a positive integer $\alpha$ called the \textit{arity}, %←arityの行だけ要らない？
\item an initial $R$-valid conformation $\sigma \in C_{\le \alpha}(\Sigma)$ called the \textit{seed}, whose first bead is assumed to be at the origin $O$ without loss of generality, 
\item a (possibly infinite) \textit{transcript} $w \in \Sigma^* \cup \Sigma^\omega$, which is to be folded upon the seed by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads. 
\end{itemize}
%
The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
The set $\mathcal{F}(\Xi)$ of conformations \textit{foldable} by the system $\Xi$ is recursively defined as: the seed $\sigma$ is in $\mathcal{F}(\Xi)$; and provided that an elongation $C_i$ of $\sigma$ by the prefix $w[1..i]$ be foldable (i.e., $C_0 = \sigma$), its further elongation $C_{i+1}$ by the next bead $w[i+1]$ is foldable if 
\begin{equation}\label{eq:OS_CF}
C_{i+1} \in \argmin_{
\substack{
C \in \mathcal{C}_{\le \alpha} s.t. \\
C_i \xrightarrow{R}_{w[i+1]}C \\
}
}
\min \Bigl\{ \Delta G(C') \Bigm|
C \xrightarrow{R}^*_{w[i+2...i+k]}C', k\le \delta, C' \in \mathcal{C}_{\le \alpha}
\Bigr\}.
\end{equation}
%
Then we say that the bead $w[i+1]$ and the bonds it forms are \textit{stabilized} according to $C_{i+1}$. 
The easiest way to understand this stabilization process should be the video available at \href{https://www.dailymotion.com/video/x3cdj35}{\tt https://www.dailymotion.com/video/x3cdj35}, in which the Turing universal oritatami system by Geary et al. \cite{GeMeScSe2018}, whose delay is 3, is running. 
Note that an arity-$\alpha$ oritatami system cannot fold any conformation of arity larger than $\alpha$. %←
A conformation foldable by $\Xi$ is \textit{terminal} if none of its elongations is foldable by $\Xi$. 
%The oritatami system $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
%A deterministic oritatami system folds into a unique terminal conformation. 
%An oritatami system with the empty rule set just folds into an arbitrary elongation of its seed nondeterministically. 
%Thus, the rule set is reasonably assumed non-empty.

@@

\subsection{General idea}
Basically, an folding process of counter is the same way as Geary et al \cite{counter2016}.
The construction proceeds in zig-zags.
Each pass is 3-rows thick and folds each part of the bead into a glider or turn module.
Each pass extends to straight while folding into glider and folds its last module folds into turn module and starts next pass.
The zig pass, folding from right to left, counts up in the current value of the counter.
The zag pass, folding from left to right, formats and copy to downward the value which the zig pass represents.

The module is semantically divided into 4 parts, called modules:
\begin{itemize}
\item Module F (beads 1--30): the Format module
\item Module L (beads 31--66): the Left-Turn module
\item Module H (bead 67--96): the Half-Adder module
\item Module R (bead 97--132): the Right-Turn module 
\end{itemize}

\subsubsection{Encoding}
The current value of the counter is encoded in standard binary with the most significant bit to the left.
Binary is encoded into a specific folding of the module F and H.
In zig pass, folding of module H corresponds to module F in a zag pass: namely H0 for 0, and H1 for 1.
In addition, start position of modules represents the carry: carry = 0 if module H starts to fold in the top row; carry = 1 if module H start to fold from the bottom row.
On the other hand in zag pass, folding of module F corresponding to module H in a zig pass: namely F0 for 0, and F1 for 1.

@@

\end{itemize}
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/svg/CounterEx5_1.pdf}
\caption{
The first zig pass.
The seed is encoded with "0", and the counter increments it by giving a carry.
Module H outputs "1" as a sum and cancels the carry.
}
\label{fig:counter1stzig}
\end{figure}

@@

In the output sum, module H has 2 types of beads representing "0" and  3 types of beads representing "1".
Then, module F is folded to F0 and F1 in Fig.~\ref{fig:formatters} according to the beads corresponding to 0 (H00, H11) and 1 (H01, H10, He1), respectively, to format beads representing a value.
\begin{figure}[h]
\begin{tabular}{c}
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.6\linewidth]{fig/svg/H00_1.pdf}
 \end{minipage}

 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.6\linewidth]{fig/svg/H01_1.pdf}

\begin{tabular}{c}
\ \\
 \begin{minipage}{0.33\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/H10_1.pdf}
 \end{minipage}

 \begin{minipage}{0.33\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/H11_1.pdf}
 \end{minipage}

  \begin{minipage}{0.33\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/He1_1.pdf}

 \end{minipage}
 \end{tabular}
 \caption{The paths of module H in zig pass}
 \label{fig:halfadders}
\end{figure}

\begin{figure}[h]
\begin{tabular}{c}
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.6\linewidth]{fig/svg/F0_1.pdf}
 \end{minipage}

@@

 \end{minipage}
 \end{tabular}
 \caption{The paths of module F in zag pass}
 \label{fig:formatters}
\end{figure}

@@

\begin{figure}[tb]
\begin{tabular}{c}
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.8\linewidth]{fig/svg/Lt_1.pdf}
 \end{minipage}

 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.8\linewidth]{fig/svg/Lbc_1.pdf}

@@

\ \\
\ \\
  \centering
   \includegraphics[width=0.4\linewidth]{fig/svg/Ltrc_1.pdf}

\begin{tabular}{c}
\ \\
\ \\
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/Lbe_1.pdf}
 \end{minipage}

  \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/Ltre_1.pdf}

@@

\section{How to implement each module with oritatami system}
Each module changes the output depending on the start position of folding and the environment.

\centering
\begin{table}[tb]
\begin{tabular}{c c c c}
\begin{minipage}{25mm}
	\centering
       \scalebox{0.5}{\includegraphics{fig/svg/bglider.pdf}}
\end{minipage} &
\begin{minipage}{25mm}
	\centering
       \scalebox{0.5}{\includegraphics{fig/svg/tglider.pdf}}
\end{minipage} &
\begin{minipage}{30mm}
	\centering
       \scalebox{0.5}{\includegraphics{fig/svg/plane.pdf}}
\end{minipage} &
\begin{minipage}{25mm}
	\centering
       \scalebox{0.5}{\includegraphics{fig/svg/spiral.pdf}}
\end{minipage}\\

\begin{minipage}{25mm}
	\centering
       \scalebox{0.5}{\includegraphics{fig/svg/horn.pdf}}
\end{minipage} &
\begin{minipage}{30mm}
	\centering
       \scalebox{0.5}{\includegraphics{fig/svg/kar.pdf}}
\end{minipage} &
\begin{minipage}{25mm}
	\centering
       \scalebox{0.5}{\includegraphics{fig/svg/roof.pdf}}
\end{minipage}\\

\begin{minipage}{25mm}
	\centering
       \scalebox{0.5}{\includegraphics{fig/svg/fault.pdf}}
\end{minipage} &
\begin{minipage}{30mm}
	\centering
       \scalebox{0.5}{\includegraphics{fig/svg/cliff.pdf}}
\end{minipage}\\

\end{tabular}
\end{table}

@@

@@

\bibliographystyle{splncs03}
\bibliography{sofsem2020}

>>>>

%\titlerunning{}
\author{
Kohei Maruyama\inst{1}\thanks{Primary corresponding author (\email{k.maruyama@uec.ac.jp})} \and
Shinnosuke Seki\inst{1,2}\thanks{Secondary corresponding author (\email{s.seki@uec.ac.jp})}
}
\institute{
The University of Electro-Communications, 
%Graduate School of Informatics and Engineering, 
1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan \and
ENS Lyon
}

@@

Counting is one of the most essential tasks for computing; as well known, it suffices to count for Turing universality \cite{Minsky1967}. 
Nature has been counting billions of days using molecular ``circadian clockwork'' which is ``as complicated and as beautiful as the wonderful chronometers developed in the 18th century''  \cite{McClung2006}. 
Nowadays, developments in molecular self-assembly technology enable us to design molecules to count. 
Evans has recently demonstrated a DNA tile self-assembly system that counts accurately in binary from a programmed initial count until it overflows \cite{EvansPhD}. 
In its foundational theory of molecular self-assembly, such binary counters have proved their versatility, being used to assemble shapes of particular size \cite{AdChGoHu2001,RothemundWinfree2000}, towards self-assembly of fractals \cite{MasudaSekiUbukata2018}, as an infinite scaffold to simulate all Turing machines in parallel in order to prove undecidability of nondeterminism in the abstract tile-assembly model \cite{BrChDoKaSe2013}, to name a few.

@@

Let $\Sigma$ be a finite alphabet, whose element should be regarded as type of abstract molecule, or \textit{beads}. 
A bead of type $a \in \Sigma$ is called an $a$-bead. 
By $\Sigma^*$ and $\Sigma^\omega$, we denote the set of finite sequences of beads and that of one-way infinite sequences of beads, respectively. 
The empty sequence is denoted by $\lambda$. 
Let $w = b_1 b_2 \cdots b_n \in \Sigma^*$ be a sequence of length $n$ for some integer $n$ and bead types $b_1, \ldots, b_n \in \Sigma$. 
The \textit{length} of $w$ is denoted by $|w|$, that is, $|w| = n$. %ここから要らない？↓やっぱり要る
For two indices $i, j$ with $1 \le i \le j \le n$, we let $w[i..j]$ refer to the subsequence $b_i b_{i+1} \cdots b_{j-1}b_j$; if $i = j$, then $w[i..i]$ is simplified as $w[i]$. 
For $k \ge 1$, $w[1..k]$ is called a \textit{prefix} of $w$.

Oritatami systems fold their transcript, which is a sequence of beads, over the triangular grid graph $\mathbb{T} = (V, E)$ cotranscriptionally. %↓
For a point $p \in V$, let $\hexagon_p^d$ denote the set of points which lie in the regular hexagon of radius $d$ centered at the point $p$. 
Note that $\hexagon_p^d$ consists of $3d(d+1)+1$ points. %←
A directed path $P = p_1 p_2 \cdots p_n$ in $\mathbb{T}$ is a sequence of \textit{pairwise-distinct} points $p_1, p_2, \ldots, p_n \in V$ such that $\{p_i, p_{i+1}\} \in E$ for all $1 \le i < n$. 
Its $i$-th point is referred to as $P[i]$. 
Now we are ready to abstract RNA single-stranded structures in the name of conformation. 
A \textit{conformation} $C$ (over $\Sigma$) is a triple $(P, w, H)$ of a directed path $P$ in $\mathbb{T}$, $w \in \Sigma^*$ of the same length as $P$, and a set of h-interactions $H \subseteq \bigl\{\{i, j\} \bigm| 1 \le i, i+2 \le j, \{P[i], P[j]\} \in E \bigr\}$. 
This is to be interpreted as the sequence $w$ being folded along the path $P$ in such a manner that its $i$-th bead $w[i]$ is placed at the $i$-th point $P[i]$ and the $i$-th and $j$-th beads are bound (by a hydrogen-bond-based interaction) if and only if $\{i, j\} \in H$. 
The condition $i+2 \le j$ represents the topological restriction that two consecutive beads along the path cannot be bound. 
The \textit{length} of $C$ is defined to be the length of its transcript $w$ (that is, equal to the length of the path $P$). 
A \textit{rule set} $R \subseteq \Sigma \times \Sigma$ is a symmetric relation over $\Sigma$, that is, for all bead types $a, b \in \Sigma$, $(a, b) \in R$ implies $(b, a) \in R$.
A bond $\{i, j\} \in H$ is \textit{valid with respect to $R$}, or simply $R$-valid, if $(w[i], w[j]) \in R$. 
This conformation $C$ is \textit{$R$-valid} if all of its bonds are $R$-valid. %↓
For an integer $\alpha \ge 1$, $C$ is \textit{of arity $\alpha$} if it contains a bead that forms $\alpha$ bonds but none of its beads forms more. 
By $\mathcal{C}_{\le \alpha}(\Sigma)$, we denote the set of all conformations over $\Sigma$ whose arity is at most $\alpha$; its argument $\Sigma$ is omitted whenever $\Sigma$ is clear from the context.

@@

An \textit{oritatami system} (OS) $\Xi$ is a tuple $(\Sigma, R, \delta, \alpha, \sigma, w)$, where $\Sigma$ and $R$ are defined as above, while
\begin{itemize}
\item a positive integer $\delta$ called the \textit{delay}, 
\item a positive integer $\alpha$ called the \textit{arity}, %←arityの行だけ要らない？
\item an initial $R$-valid conformation $\sigma \in C_{\le \alpha}(\Sigma)$ called the \textit{seed},
\item a (possibly infinite) \textit{transcript} $w \in \Sigma^* \cup \Sigma^\omega$, which is to be folded upon the seed by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads. 
\end{itemize}
%
The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
The set $\mathcal{F}(\Xi)$ of conformations \textit{foldable} by the system $\Xi$ is recursively defined as: the seed $\sigma$ is in $\mathcal{F}(\Xi)$; and provided that an elongation $C_i$ of $\sigma$ by the prefix $w[1..i]$ be foldable (i.e., $C_0 = \sigma$), its further elongation $C_{i+1}$ by the next bead $w[i+1]$ is foldable if 
\begin{equation}\label{eq:OS_CF}
C_{i+1} \in \argmin_{
\substack{
C \in \mathcal{C}_{\le \alpha} s.t. \\
C_i \xrightarrow{R}_{w[i+1]}C \\
}
}
\min \Bigl\{ \Delta G(C') \Bigm|
C \xrightarrow{R}^*_{w[i+2...i+k]}C', k\le \delta, C' \in \mathcal{C}_{\le \alpha}
\Bigr\}.
\end{equation}
%
Then we say that the bead $w[i+1]$ and the bonds it forms are \textit{stabilized} according to $C_{i+1}$. 
The easiest way to understand this stabilization process should be the video available at \href{https://www.dailymotion.com/video/x3cdj35}{\tt https://www.dailymotion.com/video/x3cdj35}, in which the Turing universal oritatami system by Geary et al. \cite{GeMeScSe2018}, whose delay is 3, is running. 
Note that an arity-$\alpha$ oritatami system cannot fold any conformation of arity larger than $\alpha$. %←
A conformation foldable by $\Xi$ is \textit{terminal} if none of its elongations is foldable by $\Xi$. 
%The oritatami system $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
%A deterministic oritatami system folds into a unique terminal conformation. 
%An oritatami system with the empty rule set just folds into an arbitrary elongation of its seed nondeterministically. 
%Thus, the rule set is reasonably assumed non-empty.

@@

\subsection{General idea}
Between two consecutive overflows, the proposed system behaves in the same way as the finite binary counter of Geary et al. \cite{GeMeScSe2019}.
Its transcript folds (downward in figures throughout this paper) in a zigzag manner macroscopically.
A zig, folding from right to left, increments the current value of the counter by 1.
The succeeding zag, folding from left to right, formats the incremented value for the sake of next zig and copies it downward.
Unlike the counter of Geary et al., when a zig encounters overflow, it does not abort but extends the current value by 1 bit.

%Each zig or zag is 3-rows thick.
%Each pass extends to straight while folding into glider and folds its last module folds into turn module and starts next pass.

The transcript of our counter is periodic.
Its period 1-2-3- $\cdots$ -132 is semantically divided into the following 4 subsequences, called \textit{modules}:
\begin{itemize}
\item 1--30: Format module or F
\item 31--66: Left-Turn module or L
\item 67--96: Half-Adder module or H
\item 97--132: Right-Turn module  or R
\end{itemize}
Modules are to play their roles in expected environments by folding into respective conformations which should be pairwise-distinct enough to be distinguishable by other modules transcribed later.
Such expected conformations are called a \textit{brick}.
For example, module F encounters only the four environments shown in Fig.~\ref{fig:formatters} where it takes the four bricks, respectively.

\subsubsection{Encoding}
The binary representation of the initial value, $b_{k-1} b_{k-2} \cdots b_1 b_0$ is encoded on the seed in the following format
\begin{equation} \label{eq:zagencoding}
64{-}65{-}66{-}\left( \prod^0_{i = k-1} \bigl(  w_{Hn} w_{Rb} w_{Fb_i} w_{Lbn} \bigr) \right) w_{Hn}
\end{equation}
where $w_{Hn}, w_{Rb}, w_{Fb_i}, w_{Lbn}$ are sequences of bead types exposed downward by modules H, R, F, L when they fold into bricks Hn, Rb, F$b_i$, Lbn, respectively; these bricks can be found in Figs.~\ref{fig:halfadders},\ref{fig:rightturns}, \ref{fig:formatters}, and \ref{fig:leftturns}.
%$w_{Hn} = 67{-}76{-}77{-}78{-}79{-}88{-}89{-}90{-}91{-}96$ \\
%$w_{Rb} = 97{-}102{-}103{-}108{-}109{-}114{-}115{-}120{-}121{-}126{-}127{-}132$\\
%$w_{Lbn} = 31{-}36{-}37{-}42{-}43{-}48{-}49{-}54{-}55{-}64{-}65{-}66$

%64 65 66
%67 76 77 78 79 88 89 90 91 96
%97 102 103 108 109 114 115 120 121 126 127 132
%
%1 10 11 12 13 22 23 24 25 30
%
%31 36 37 42 43 48 49 54 55 64 65 66
%67 76 77 78 79 88 89 90 91 96
%97 108 109 120

The current value of the counter is encoded in standard binary with the most significant bit to the left.
Binary is encoded into a specific folding of the module F and H.
In zig pass, folding of module H corresponds to module F in a zag pass: namely H0 for 0, and H1 for 1.
In addition, start position of modules represents the carry: carry = 0 if module H starts to fold in the top row; carry = 1 if module H start to fold from the bottom row.
On the other hand in zag pass, folding of module F corresponding to module H in a zig pass: namely F0 for 0, and F1 for 1.

@@

\end{itemize}
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/svg/CounterEx5_1.pdf}
\caption{
The first zig pass.
The seed is encoded with "0" same as bottom of F0(
\textcircled{\scriptsize 1}{-}\textcircled{\scriptsize 10}{-}\textcircled{\scriptsize 11}{-}\textcircled{\scriptsize 12}{-}\textcircled{\scriptsize 13}{-}\textcircled{\scriptsize 22}{-}\textcircled{\scriptsize 23}{-}\textcircled{\scriptsize 24}{-}\textcircled{\scriptsize 25}{-}\textcircled{\scriptsize 30}),
 and the counter increments it by giving a carry.
Module H outputs "1" as a sum and cancels the carry.
}
\label{fig:counter1stzig}
\end{figure}

@@

In the output sum, module H has 2 types of beads representing "0" and  3 types of beads representing "1".
Then, module F is folded to F0 and F1 in Fig.~\ref{fig:formatters} according to the beads corresponding to 0 (H00, H11) and 1 (H01, H10, He1), respectively, to format beads representing a value.
\begin{figure}[h]
\begin{tabular}{c}
 \begin{minipage}{0.3\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/H00_1.pdf}
 \end{minipage}

 \begin{minipage}{0.3\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/H01_1.pdf}

 \end{minipage}

  \begin{minipage}{0.3\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/He1_1.pdf}
 \end{minipage}
 \end{tabular}

\begin{tabular}{c}
\ \\
 \begin{minipage}{0.3\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/H10_1.pdf}
 \end{minipage}

 \begin{minipage}{0.3\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/H11_1.pdf}
 \end{minipage}

  \begin{minipage}{0.3\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/Hn_1.pdf}

 \end{minipage}
 \end{tabular}
 \caption{All the 6 bricks of Module H. In zags, H always folds into the bottom-right brick Hn. }
 \label{fig:halfadders}
\end{figure}

\begin{figure}[h]
\begin{tabular}{c}
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.6\linewidth]{fig/svg/Fnt_1.pdf}
 \end{minipage}

 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.6\linewidth]{fig/svg/Fnb_1.pdf}

 \end{minipage}
 \end{tabular}
\ \\
\ \\
\begin{tabular}{c}
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.6\linewidth]{fig/svg/F0_1.pdf}
 \end{minipage}

@@

 \end{minipage}
 \end{tabular}
 \caption{All the 4 bricks of Module F: The 2 bricks at the top are for zigs while the 2 bottom are for zags. }
 \label{fig:formatters}
\end{figure}

@@

\begin{figure}[tb]
\begin{tabular}{c}
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.8\linewidth]{fig/svg/Lt_3.pdf}
 \end{minipage}

 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.8\linewidth]{fig/svg/Lbc_3.pdf}

@@

\ \\
\ \\
  \centering
   \includegraphics[width=0.4\linewidth]{fig/svg/Ltrc_3.pdf}

\begin{tabular}{c}
\ \\
\ \\
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/Lbe_3.pdf}
 \end{minipage}

  \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/Ltre_3.pdf}

@@

\begin{figure}[tb]
\begin{tabular}{c}
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.8\linewidth]{fig/svg/Rt_1.pdf}
 \end{minipage}

 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.8\linewidth]{fig/svg/Rb_1.pdf}

 \end{minipage}

\vspace{10mm}

\ \\
  \raggedright
   \includegraphics[width=0.3\linewidth]{fig/svg/Rtr_1.pdf}

 \end{tabular}
 \caption{The paths of module R}
 \label{fig:rightturns}
\end{figure}

\section{The brick automaton}
Beads which has already been folded around, that is, the environment decide which module transcript will be.
The environmental transition is represented Fig.~\ref{fig:brickautomaton}.
In addition, each symbol written as a state transition is conformation such as Fig.~\ref{fig:transitionconformation}
%\centering
%\begin{table}[tb]
%\begin{tabular}{c c c c}
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/bglider.pdf}}
%\end{minipage} &
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/tglider.pdf}}
%\end{minipage} &
%\begin{minipage}{30mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/plane.pdf}}
%\end{minipage} &
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/spiral.pdf}}
%\end{minipage}\\
%
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/horn.pdf}}
%\end{minipage} &
%\begin{minipage}{30mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/kar.pdf}}
%\end{minipage} &
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/roof.pdf}}
%\end{minipage}\\
%
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/fault.pdf}}
%\end{minipage} &
%\begin{minipage}{30mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/cliff.pdf}}
%\end{minipage}\\
%
%\end{tabular}
%\end{table}

\begin{figure}[tb]
\centering
\includegraphics[width=\textwidth]{fig/svg/inf-ai_c_2.pdf}
\vspace*{5mm}

\scalebox{0.8}{
\begin{tikzpicture}
	\node[anchor=north, inner sep=0] (tg) at (0,0) {
 		   \includegraphics[width=0.2\textwidth]{fig/svg/tglider.pdf}
	};
	\node[anchor=north, inner sep=0] (bg) at (3,0) {
 		   \includegraphics[width=0.2\textwidth]{fig/svg/bglider.pdf}
	};
	\node[anchor=north, inner sep=0] (pl) at (6,0) {
 		   \includegraphics[width=0.2\textwidth]{fig/svg/plane.pdf}
	};
	\node[anchor=north, inner sep=0] (sp) at (9,0) {
 		   \includegraphics[width=0.2\textwidth]{fig/svg/spiral.pdf}
	};

	\node[anchor=north, inner sep=0] (ho) at (-1.5,-3) {
 		   \includegraphics[width=0.2\textwidth]{fig/svg/horn.pdf}
	};
	\node[anchor=north, inner sep=0] (ka) at (1.5,-3) {
 		   \includegraphics[width=0.15\textwidth]{fig/svg/kar.pdf}
	};
	\node[anchor=north, inner sep=0] (ro) at (4.5,-3) {
 		   \includegraphics[width=0.2\textwidth]{fig/svg/roof.pdf}
	};
	\node[anchor=north, inner sep=0] (fa) at (7.5,-3) {
 		   \includegraphics[width=0.2\textwidth]{fig/svg/fault.pdf}
	};
	\node[anchor=north, inner sep=0] (ci) at (10.5,-3) {
 		   \includegraphics[width=0.2\textwidth]{fig/svg/cliff.pdf}
	};

	\node[below, shift=(-90:0.8)] at (tg) {t};
	\node[below, shift=(-90:0.8)] at (bg) {b};
	\node[below, shift=(-90:0.8)] at (pl) {p};
	\node[below, shift=(-90:0.8)] at (sp) {s};

	\node[below, shift=(-90:1)] at (ho) {h};
	\node[below, shift=(-90:1)] at (ka) {k};
	\node[below, shift=(-90:0.8)] at (ro) {r};
	\node[below, shift=(-90:0.8)] at (fa) {f};
	\node[below, shift=(-90:0.8)] at (ci) {c};
\end{tikzpicture}
}
%\caption{Transition conformations}
%\label{fig:transitionconformation}
%\end{figure}

%\begin{figure}[tb]
\caption{The brick automaton of infinite binary counter}
\label{fig:brickautomaton}
\end{figure}

@@

\bibitem{GeMeScSe2018}
Cody Geary and Pierre-\'Etienne Meunier and Nicolas Schabanel and Shinonsuke Seki,
Proving the {T}uring Universality of Oritatami Cotranscriptional Folding,
Proc. ISAAC 2018,
23:1 -- 23:13,2018.

@@
